Constructing a universe for the setoid model

### 2020-10-13 paper.tex
Add brief clarification on inU~
small fixes abstract

Although already a rich theory as currently defined, SeTT currently lacks a way
to internalize the notion of type beyond propositions. This paper is a step
towards extending SeTT with a universe of setoids.
%
To this aim, we present the construction of a (non-univalent) universe of
setoids within the setoid model, first as an inductive-recursive definition,
which is then translated to an inductive-inductive definition and finally to an
inductive family. These translations from more powerful definition schemas to
simpler ones ensure that our construction can still be defined in a relatively
small metatheory, that however must include a proof-irrelevant identity type
with a strong transport rule. \keywords{type theory \and
  function extensionality \and univalence \and setoid model \and
  induction-recursion \and induction-induction}
\end{abstract}

@@

Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}

>>>>

Although already a rich theory as currently defined, SeTT currently lacks a way
to internalize the notion of type beyond propositions, hence we want
to extend SeTT with a universe of setoids.
%
To this aim, we present the construction of a (non-univalent) universe of
setoids within the setoid model, first as an inductive-recursive definition,
which is then translated to an inductive-inductive definition and finally to an
inductive family. These translations from more powerful definition schemas to
simpler ones ensure that our construction can still be defined in a relatively
small metatheory which includes a proof-irrelevant identity type
with a strong transport rule.

\keywords{type theory \and
  function extensionality \and univalence \and setoid model \and
  induction-recursion \and induction-induction}
\end{abstract}

@@

Just as the role of $\inU$ is, as before, to classify all types that are image
of $\El$, in the same way $\inUU\ p\ q$ classifies all relations of type $A \to
A' \to \mProp$ that are image of $\_\vdash\_\sim_{\El}\_$,
given proofs $p : \inU\ A, q : \inU\ A'$.
%
Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}
